---
title: "**CalfSim Report**"
output: html_document
params:
  teste: 'NULL'
  all_data: 'NULL'
      
---


<style type = "text/css">

body{ /* Normal  */
      font-family: Helvetica;
      font-size: 12px;
      color: Grey;
        
  }
td {  /* Table  */
  font-family: Helvetica;
  font-size: 12px;
  text-align: center;
}
h1.title {
  font-family: Helvetica;
  font-size: 30px;
  color: #007582;
}
h1 { /* Header 1 */
  font-family: Helvetica;
  font-size: 24px;
  color: #007582;
  text-align: center;

}
h2 { /* Header 2 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
 
}
h3 { /* Header 3 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
  
}
code.r{ /* Code block */
    font-family: Helvetica;
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-family: Helvetica;
    font-size: 14px;
}
</style>

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 50%;
  text-align: center;
}

</style>

## Calf Inputs

Report under development...

```{r, echo = FALSE}

params$teste |> 
  kableExtra::kbl(row.names = FALSE, align = "l") |> 
  kableExtra::column_spec(1, bold = TRUE) |> 
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582") |> 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## Performance 

```{r, echo = FALSE}

p1 <- params$all_data |> 
  scenario_plot(var_y = "BW_cor")

p2 <- params$all_data |> 
  scenario_plot(var_y = "ADG")

echarts4r::e_arrange(p1, p2, rows = 1, cols = 2)

```

```{r, echo = FALSE}

# params$all_data |> 
#   head() |> 
#   kableExtra::kbl(row.names = FALSE, align = "l") |> 
#   kableExtra::column_spec(1, bold = TRUE) |> 
#   kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582") |> 
#   kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

<hr />
<p style = "text-align: center; color: #007582;"> All rights reserved - University of Vermont </p>
<center>

```{r, warning = FALSE, echo = FALSE}

path_logo <- system.file("app/www", "costaslablogo.jpeg", package = "CalfSim")

htmltools::img(
   src = knitr::image_uri(path_logo),
   style = "width:100px; height:85px;")
   
```
</center>
&nbsp;





